Stateless Model Checking with Data-Race Preemption Points

### 2016-07-16 oopsla-16/evaluation.tex
show icb bound distribution stats

>>>>

\revisionx{
To ensure that our corpus of P2 and Pintos bugs gives an unbiased comparison between \quicksand~and ICB,
we also counted the preemption bounds necessary for ICB to find each of its bugs.
Table~\ref{tab:icb-bounds} shows the distribution of these bounds,
which is consistent with the results of \cite{chess-icb}.
%justifies that our portrayal of ICB is fair.
%and shows no bias towards requiring high preemption bounds.
}

\begin{table}[h]
	\begin{center}
		\revisionx{
		\small
	\begin{tabular}{r|c|c}
		{\bf Bound} & {\bf SSS-MC-ICB} & {\bf SSS-MC-Shared-Mem} \\
		\hline
		0	& 2	& 1	\\
		1	& 82	& 86	\\
		2	& 15	& 32	\\
		3	& 2	& 3	\\
		4+	& 0	& 0	\\
	\end{tabular}
		}
	\end{center}
	\label{tab:icb-bounds}
	\caption{\revisionx{Distribution of preemption bounds among bugs found by ICB \cite{chess-icb} control experiments. (Bound 0 means the bug was found by switching threads only on {\tt yield()}s.)}}
\end{table}
